% Submission-ready anonymized ACM template
% Use the `anonymous` and `review` options for blinded review.
% For final camera-ready, remove `anonymous` and `review` and fill in metadata.
\documentclass[manuscript,review,anonymous]{acmart}

% If your conference/journal gives a submission ID, put it here (optional)
% \acmSubmissionID{123-A56-BU3}

% Do NOT add author metadata here when anonymizing.
% Remove acknowledgments and any self-identifying information.
% For references to your own prior work, either redact identifying parts
% or phrase them in the third person as required by the venue.

\begin{document}
\title{A Minimal Anonymized Submission Using the acmart Class}

\begin{abstract}
This document is a minimal anonymized submission template using the
`acmart` class. It demonstrates the `manuscript,review,anonymous` options
and suggests practices for anonymized submissions.
\end{abstract}

% No \maketitle author block for anonymous submissions; \maketitle prints
% the title and abstract only when no authors are provided.
\maketitle

\section{Introduction}
This is a short introduction. For submissions, make sure to remove
self-identifying material (institutional names, grant numbers, author
names in acknowledgements, etc.).

\section{Related Work}
Cite relevant work as usual \cite{DBLP:books/mk/GrayR99}. If you must
cite your own prior work, follow the venue's anonymization policy: some
venues allow citing your work in third person ("Prior work by the
authors [XX]") while others require redaction.

\section{Submission checklist notes}
- No author names or affiliations are present.
- Remove Acknowledgements before submission.
- Avoid uploading supplementary material containing identifying metadata.

\section{Conclusion}
Short conclusion.

% Bibliography: point to a sample .bib in the repository
\bibliographystyle{ACM-Reference-Format}
\bibliography{samples/sample-base}

\end{document}
